---
title: "Identifiability in Linear Mixed Effect Models"
subtitle: "Based on Wang2013"
author: "Peter von Rohr"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
met <- rmdhelp::MendeleyExportToolR6$new()
met$set_local_bib_file(ps_local_bib_file = 'skeleton.bib')
met$set_this_rmd_file(ps_this_rmd_file = ifelse(rstudioapi::isAvailable(),
    rstudioapi::getActiveDocumentContext()$path, rprojroot::thisfile()))

```

# Disclaimer
The topic of identifiability in linear mixed effect model (LME) is summarized based on `r met$add('Wang2013')`. 


# Introduction
In LME, the response variable is decomposed into three parts. 

1. the design matrix associated with fixed effects and covariables right-multiplied by a vector of unknown fixed effects and covariables 
2. the random effects left-multiplied by a design matrix and 
3. a random residual vector



```{r, echo=FALSE, results='asis'}
if (!knitr::is_html_output()) cat('# References\n')
```


